\section{experience}
\begin{entrylist}
%------------------------------------------------
\entry
{JAGEX GAMES STUDIO}
{08/2014--09/2014}
{
\emph{Junior Web Systems Developer}
\begin{itemize}[topsep=0pt]
\item Designed and developed a testing framework and tests for internal web applications. Tests were integrated with a build automation system to provide early detection of errors in business critical systems. Framework has since been used by other members of Web Systems QA on other projects.
\end{itemize}
}
%------------------------------------------------
\entry
{GEOSPOCK LTD.}
{07/2013--09/2013}
{
\emph{Industrial Placement Student}
\begin{itemize}[topsep=0pt]
\item Designed and developed Python Google App Engine REST Service and Android client. Features implemented included user account management, file up/download capabilities and geo-location functions.
\end{itemize}
}
%------------------------------------------------
\entry
{PHILIPS RESEARCH UK}
{07/2012--07/2013}
{
\emph{Industrial Placement Student}\\
\muted{Amazon Web Services (AWS) Analysis and Evaluation}
\begin{itemize}[topsep=0pt]
\item Determined the viability of using AWS Elastic Compute Cloud for deployment of an existing large enterprise system. Evaluated various Platform-as-a-Service systems.
\end{itemize}

\muted{Telehealth Video Conferencing Prototype}
\begin{itemize}[topsep=0pt]
\item Designed and developed a client to access a third-party SOAP based video conferencing web service. Integrated with existing product for demonstration by Philips business and NHS personnel.
\end{itemize}

\muted{Telehealth System Enhancements}
\begin{itemize}
\item Designed, developed and tested patches for an existing telehealth system. Improvements included security enhancements, REST API extensions and database improvements. Also responsible for set up and maintenance of development environments.
\end{itemize}}
\end{entrylist}